Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-10-11 cvx-flats-neurips21/cvx-flats.tex
Removing typo in line 64
rates
Fixing notation omissions and adding an informal consistency definition

\documentclass[11pt]{article} % Anonymized submission
% \renewcommand{\includegraphics}[1][1]{}

\usepackage[nonatbib]{neurips_2021}

@@

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
%\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\definecolor{myblue}{rgb}{0,0.3,0.8} \definecolor{myorange}{rgb}{0.9,0.5,0}
\usepackage{wrapfig}
\usepackage[small]{caption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\author{%
	Jessie Finocchiaro\thanks{Use footnote for providing further information
		about author (webpage, alternative address)---\emph{not} for acknowledging
		funding agencies.} \\
	Department of Computer Science\\
	CU Boulder\\
	\texttt{jefi8453@colorado.edu} \\
	% examples of more authors
	\And
	Raf Frongillo \\
	CU Boulder \\
	\texttt{raf@colorado.edu} \\
	\AND
	Bo Waggoner\\
	CU Boulder \\
	\texttt{bwag@colorado.edu} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir})~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
%\jessiet{Do we still want this following paragraph?}
%\raft{Good question.  I edited a bit, but still up for discussion.}
%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
\begin{table}[h!]
  \vspace*{10pt}
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
%      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification\\ 
      \cmidrule{2-3}
%      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3}, e.g. least-squares regression & \textbf{Q4}, e.g. variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}\vspace*{-5pt}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.\vspace*{-10pt}}
    \label{tab:quadrants}
  \end{center}
\end{table}
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[yscale=0.6,xscale=0.46]

@@

    \path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (15.8,3) -- (15.8,-3) -- cycle;
    \draw[dashed, opacity = 0.3] (0,-3) -- (0,-0.1);
    \draw[dashed, opacity = 0.3] (0,3) -- (0,0.6);
    \node[draw=none] at (3,2.5) {{\large$\Lcvx$}};
    \node[draw=none] at (-3,2.5) {{\large$\L$}};

@@

    % edges
    \path[->,bend angle=10]
    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
    (calibrated) edge[bend right] (indir-elic)
    (indir-elic) edge node[above, sloped]{Thm.~\ref{thm:convex-flats-inf-dim}} (d-flats)
    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
  \end{tikzpicture}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results for Q1, while simultaneously applying to other quadrants. We illustrate the breadth and power of $d$-flats by resolving two open questions for Q3 and Q4 in \S~\ref{sec:contin-consis}.}
\label{fig:results-flow}
\end{figure}
Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
paragraph
See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.

@@

As definitions of consistency are difficult to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g. Quadrants 1 and 3. 
Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1.
%, where one is given a target statistic \raf{loss?} and discrete prediction set
We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Theorem~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

In supervised learning, data is drawn from a distribution $\D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
Here $\X$ is the \emph{feature space}, $\Y$ the \emph{label space}, and $\R$ the \emph{report} or \emph{prediction space}, possibly different from $\Y$.
%consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
%The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems, $\R$ may be all $|\Y|!$ permutations over the $|\Y|$ labels forming $\Y$.
We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
We can often abstract away $x$, working directly with a set of (conditional) distributions over outcomes $\P \subseteq \simplex$.
We then write e.g.\ $\E_p \ell(r,Y)$ to mean the expected loss of prediction $r \in \R$ when $Y\sim p$.

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
In this case, $d$ is the prediction dimension of $d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
(See \S~\ref{app:minnable-assumption} for a discussion of this assumption.)
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
%Typically, we notate finite report sets $\R$.

@@

\begin{SCfigure}
	\centering
	\begin{tikzpicture}[yscale=0.6]
\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=2pt, fill = white];
\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=2pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
\tikzstyle{every node}=[font=\small];

% vertices
\node[vertex] (speech) at  (0,2) {Speech};
\node[vertexblue] (active) at  (-2,1) {Active};
\node[vertex] (nonactive) at  (2,1) {Non-active};
\node[vertexblue] (median) at  (1,0) {Median};
\node[vertexblue] (passive) at  (3,0) {Passive};

@@

      \begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
	\node at (point) {$\bullet$};
	% \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
      \end{scope}
      % \node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
      \node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
      % \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
      \placefiglabel{(Q1)}
    \end{tikzpicture}
    &
      \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
          \clip (h) -- (m) -- (l) -- (h);
          \draw[myblue,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
          \def\e{1/16};
          \draw[myblue,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
          \coordinate (point) at (0.3,0.4, 0.3);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
          \node at (point) {$\bullet$};
          % \draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
          % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	% \node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
	% \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	% \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
      \end{tikzpicture}
      \hspace*{-10pt}
    \\
    \hline
    \hspace*{-10pt}
    \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
      % standard tikz coordinate definition using x, y, z coords
      \coordinate (orig) at (0,0,0);

@@

      \begin{scope}
        \clip (h) -- (m) -- (l) -- (h);
        \foreach \c in {0,0.05,...,1}
        {
          \pgfmathsetmacro\aa{\c}
          \coordinate (A) at ($(\aa,1-\aa,0)$);
          \coordinate (B) at ($(\aa,1-\aa,2)$);
          \draw[myblue,thin] (A) -- (B);
        }
        \draw[myblue] (0.45,0.55,0) -- (0.45,.55,2);
        \draw[myorange, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
        % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
      \end{scope}
      \node (point) at (0.3,0.4,0.3) {$\bullet$};
      \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.1}\!$};
      % \node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
      \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
      \placefiglabel{(Q3)}
    \end{tikzpicture}
    &
      \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
        % standard tikz coordinate definition using x, y, z coords
        \coordinate (orig) at (0,0,0);

@@

\paragraph{Broader Impacts via influence on downstream research.}
\jessiet{Taken from original BI statement for this paper}
This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
The theory in this paper may help practitioners in a number of ways.
Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.

>>>>

\documentclass{article} % Anonymized submission
% \renewcommand{\includegraphics}[1][1]{}

\usepackage[nonatbib,final]{neurips_2021}

@@

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
%\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\definecolor{myblue}{rgb}{0,0.3,0.8} 
\definecolor{mygreen}{rgb}{0,0.8,0.2}
\definecolor{myorange}{rgb}{0.9,0.5,0}
\usepackage{wrapfig}
\usepackage[small]{caption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\author{%
	Jessie Finocchiaro\\%\thanks{Use footnote for providing further information
		%about author (webpage, alternative address)---\emph{not} for acknowledging
	%	funding agencies.} \\
	%Department of Computer Science\\
	CU Boulder\\
	\texttt{jefi8453@colorado.edu} \\
	% examples of more authors
	\And
	Raf Frongillo \\
	CU Boulder \\
	\texttt{raf@colorado.edu} \\
	\AND
	Bo Waggoner\\
	CU Boulder \\
	\texttt{bwag@colorado.edu} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

\begin{definition}[Consistent: loss, informal]\label{def:consistent-ell-informal}
	A loss $L \in \L$ and link $(L,\psi)$ are \emph{consistent} with respect to a target loss $\ell$ if, for all distributions $D$ over $\X \times \Y$ and all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}

When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir}) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
%\jessiet{Do we still want this following paragraph?}
%\raft{Good question.  I edited a bit, but still up for discussion.}
%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
\begin{table}[h!]
  \vspace*{10pt}
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
%      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification\\ 
      \cmidrule{2-3}
%      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3}, e.g. least-squares regression & \textbf{Q4}, e.g. variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}\vspace*{-5pt}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.\vspace*{-10pt}}
    \label{tab:quadrants}
  \end{center}
\end{table}
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[yscale=0.6,xscale=0.46]

@@

    \path[fill=mygreen, fill opacity = 0.1] (0,-3) -- (0,3) -- (15.8,3) -- (15.8,-3) -- cycle;
    \draw[dashed, opacity = 0.3] (0,-3) -- (0,-0.1);
    \draw[dashed, opacity = 0.3] (0,3) -- (0,0.6);
    \node[draw=none] at (3,2.5) {{\large$\Lcvx$}};
    \node[draw=none] at (-3,2.5) {{\large$\L$}};

@@

    % edges
    \path[->,bend angle=10]
    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
    (calibrated) edge[bend right] (indir-elic)
    (indir-elic) edge node[above, sloped]{Thm.~\ref{thm:convex-flats-inf-dim}} (d-flats)
    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
  \end{tikzpicture}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results for Q1, while simultaneously applying to other quadrants. We illustrate the breadth and power of $d$-flats by resolving two open questions for Q3 and Q4 in \S~\ref{sec:contin-consis}.}
\label{fig:results-flow}
\end{figure}
Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.

@@

As definitions of consistency are difficult to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g. Quadrants 1 and 3. 
Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1.
%, where one is given a target statistic \raf{loss?} and discrete prediction set
We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Proposition~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

In supervised learning, data is drawn from a distribution $\D$ over the space $\X \times \Y$ and the goal is to produce a hypothesis $f: \X \to \R$.
Here $\X$ is the \emph{feature space}, $\Y$ the \emph{label space}, and $\R$ the \emph{report} or \emph{prediction space}, possibly different from $\Y$.
%consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
%The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems, $\R$ may be all $|\Y|!$ permutations over the $|\Y|$ labels forming $\Y$.
We focus on surrogate losses, target problems, and their relationships to conditional distributions $p := \D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$.
We can often abstract away $x$, working directly with a set of (conditional) distributions over outcomes $\P \subseteq \simplex$, where $\simplex := \{p \in \reals^{|\Y|}_+ \mid \|p\|= 1\}$ is the probability simplex over labels.
We then write e.g.\ $\E_p \ell(r,Y)$ to mean the expected loss of prediction $r \in \R$ when $Y\sim p$.

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
In this case, $d$ is the prediction dimension of $d$.
We write $\L_d $ for the set of (Borel) $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
(See \S~\ref{app:minnable-assumption} for a discussion of this assumption.)
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
%Typically, we notate finite report sets $\R$.

@@

\begin{SCfigure}
	\centering
	\begin{tikzpicture}[yscale=0.6]
\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=2pt, fill = white];
\tikzstyle{vertexgrn} = [draw, minimum width=4em, inner sep=2pt, fill = green, fill opacity = 0.2, text=black, text opacity = 1.];
\tikzstyle{every node}=[font=\small];

% vertices
\node[vertex] (speech) at  (0,2) {Speech};
\node[vertexgrn] (active) at  (-2,1) {Active};
\node[vertex] (nonactive) at  (2,1) {Non-active};
\node[vertexgrn] (median) at  (1,0) {Median};
\node[vertexgrn] (passive) at  (3,0) {Passive};

@@

      \begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[mygreen] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[mygreen] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[mygreen] (0,1/2,1/2) -- (1/2,1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
	\node at (point) {$\bullet$};
	% \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
      \end{scope}
      % \node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
      \node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
      % \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
      \placefiglabel{(Q1)}
    \end{tikzpicture}
    &
      \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
          \clip (h) -- (m) -- (l) -- (h);
          \draw[mygreen,thick] (1/2,0,1/2) -- (0,1/2, 1/2);
          \def\e{1/16};
          \draw[mygreen,thick] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
          \coordinate (point) at (0.3,0.4, 0.3);
          \draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
          \draw[myblue, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
          \node at (point) {$\bullet$};
          % \draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
          % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	% \node[inner sep=2pt] (levsetmin1) at (0.6, .2,.2) {$\gamma_{\text{passive}}$};
	\node[inner sep=2pt] (levset1) at (.2,0.6,.2) {$\gamma_{\text{median}}$};
	% \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	% \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
      \end{tikzpicture}
      \hspace*{-10pt}
    \\
    \hline
    \hspace*{-10pt}
    \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
      % standard tikz coordinate definition using x, y, z coords
      \coordinate (orig) at (0,0,0);

@@

      \begin{scope}
        \clip (h) -- (m) -- (l) -- (h);
        \foreach \c in {0,0.05,...,1}
        {
          \pgfmathsetmacro\aa{\c}
          \coordinate (A) at ($(\aa,1-\aa,0)$);
          \coordinate (B) at ($(\aa,1-\aa,2)$);
          \draw[mygreen,thin] (A) -- (B);
        }
        \draw[mygreen] (0.45,0.55,0) -- (0.45,.55,2);
        \draw[myblue, very thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
        % \draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
      \end{scope}
      \node (point) at (0.3,0.4,0.3) {$\bullet$};
      \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.1}\!$};
      % \node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
      % \draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
      \draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
      \placefiglabel{(Q3)}
    \end{tikzpicture}
    &
      \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
        % standard tikz coordinate definition using x, y, z coords
        \coordinate (orig) at (0,0,0);

@@
